---
title: "Experiment Simulation"
author: "Frédéric"
date: "18 septembre 2018"
output: pdf_document
header-includes:
   - \usepackage{booktabs}
   - \usepackage{subfig}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(weights)
```


```{r comment=NA, echo=FALSE, message=FALSE}
# Nombre de participants
set.seed(1234)
n <- 100
# Mémoire : scores [0:10]
mem_mean <- 5
mem_sd   <- 2
# Compréhension code de surface [0:15]
comp_C_mean <- 10
comp_C_sd   <- 3
# Compréhension sémantique [0:15]
comp_S_mean <- 9
comp_S_sd   <- 3
# Compréhension inférences [0:15]
comp_I_mean <- 8
comp_I_sd   <- 3


data <- data.frame (ID=1:n)
data$sexe <- as.factor(sample(c(1,2), n, replace=TRUE))
data$age <-  sample(18:25, n, replace=TRUE)
data$signal <- as.factor(sample(c('n', 'v', 't'), n, replace = TRUE))
data$task <- as.factor(sample(c('c', 'v', 's', 't'), n, replace = TRUE))

data$memory <- round (rnorm (n, mem_mean, mem_sd), 0)
data$memory[data$memory < 0] <- 0
data$memory[data$memory > 10] <- 10

data$comp_C <- round (rnorm (n, comp_C_mean, comp_C_sd), 0)
data$comp_C[data$comp_C < 0] <- 0
data$comp_C[data$comp_C > 15] <- 15

data$comp_S <- round (rnorm (n, comp_S_mean, comp_S_sd), 0)
data$comp_S[data$comp_S < 0] <- 0
data$comp_S[data$comp_S > 15] <- 15

data$comp_I <- round (rnorm (n, comp_I_mean, comp_I_sd), 0)
data$comp_I[data$comp_I < 0] <- 0
data$comp_I[data$comp_I > 15] <- 15

count <- matrix(c(1,2,3,4,5, 6, 7, 8, 9, 10, 11, 12), nrow = 4)
count[1,1] <- nrow (subset(data, signal=='n' & task=='c'))
count[1,2] <- nrow (subset(data, signal=='v' & task=='c'))
count[1,3] <- nrow (subset(data, signal=='t' & task=='c'))
count[2,1] <- nrow (subset(data, signal=='n' & task=='t'))
count[2,2] <- nrow (subset(data, signal=='v' & task=='t'))
count[2,3] <- nrow (subset(data, signal=='t' & task=='t'))
count[3,1] <- nrow (subset(data, signal=='n' & task=='v'))
count[3,2] <- nrow (subset(data, signal=='v' & task=='v'))
count[3,3] <- nrow (subset(data, signal=='t' & task=='v'))
count[4,1] <- nrow (subset(data, signal=='n' & task=='s'))
count[4,2] <- nrow (subset(data, signal=='v' & task=='s'))
count[4,3] <- nrow (subset(data, signal=='t' & task=='s'))

f <- fisher.test(count)
```

## Simulation datas

`r n` participants datas were randomly simulated : `r length(which(data$sexe == 1))` men and `r length(which(data$sexe == 2))` women. Mean age was `r round(mean(data$age),1)` (SD = `r round(sd(data$age),1)`). Participants repartition didn't significantly differ across conditions (Table \ref{tab:repartition}, Fisher's Exact Test for Count Data, \textit{p} = `r rd(f$p.value, 3)`).

\begin{table}[h]
\centering
\begin{tabular}{ c c c c c}
  \toprule
   Task & \multicolumn{3}{c}{Signal} \\
   \cmidrule(lr){2-4}
   & none  & visual & textual & Total \\
   \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5}
  Control & `r nrow (subset(data, signal=='n' & task=='c'))` & `r nrow (subset(data, signal=='v' & task=='c'))` & `r nrow (subset(data, signal=='t' & task=='c'))` & `r nrow (subset(data, task=='c'))`\\
  Verbal & `r nrow (subset(data, signal=='n' & task=='t'))` & `r nrow (subset(data, signal=='v' & task=='t'))` & `r nrow (subset(data, signal=='t' & task=='t'))` & `r nrow (subset(data, task=='t'))`\\
  Visual & `r nrow (subset(data, signal=='n' & task=='v'))` & `r nrow (subset(data, signal=='v' & task=='v'))` & `r nrow (subset(data, signal=='t' & task=='v'))` & `r nrow (subset(data, task=='v'))`\\
  Spatial & `r nrow (subset(data, signal=='n' & task=='s'))` & `r nrow (subset(data, signal=='v' & task=='s'))` & `r nrow (subset(data, signal=='t' & task=='s'))` & `r nrow (subset(data, task=='s'))`\\
  \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5}
  Total & `r nrow (subset(data, signal=='n'))` & `r nrow (subset(data, signal=='v'))` & `r nrow (subset(data, signal=='t'))` & `r n` \\
  \bottomrule
\end{tabular}
\caption{Participants repartition across conditions}
\label{tab:repartition}
\end{table}

<!-- to label figure : -->
<!-- see https://rosannavanhespenresearch.wordpress.com/2016/03/18/writing-your-thesis-with-r-markdown-3-figures-r-code-and-tables/ -->


  ```{r fig.cap = "figure caption. \\label{figurelabel}", echo=FALSE}
  oldpar <- par(mfrow=c(2,2), oma = c( 0, 0, 0, 0 ))
  plot(density(data$memory), main="", xlab="Memory", ylab="")
  plot(density(data$comp_C), main="", xlab="Surface comprehension", ylab="")
  plot(density(data$comp_S), main="", xlab="Semantic comprehension", ylab="")
  plot(density(data$comp_I), main="", xlab="Inference comprehension", ylab="")
  par(oldpar)
  
  ```

## Performances

\begin{table}[h]
\centering
\subfloat[Memory]{\begin{tabular}{ c c c c c}
  \toprule
   Task & \multicolumn{3}{c}{Signal} \\
   \cmidrule(lr){2-4}
   & none  & visual & textual & All \\
   \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5}
  Control & `r format(mean(subset(data, signal=='n' & task=='c')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='c')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='c')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='c')$memory),digits = 2, nsmall = 2)`\\
  Verbal & `r format(mean(subset(data, signal=='n' & task=='t')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='t')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='t')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='t')$memory),digits = 2, nsmall = 2)`\\
  Visual & `r format(mean(subset(data, signal=='n' & task=='v')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='v')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='v')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='v')$memory),digits = 2, nsmall = 2)`\\
  Spatial & `r format(mean(subset(data, signal=='n' & task=='s')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='s')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='s')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='s')$memory),digits = 2, nsmall = 2)`\\
  \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5}
  All & `r format(mean(subset(data, signal=='n')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v')$memory),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t')$memory),digits = 2, nsmall = 2)` & `r format(mean(data$memory),digits = 2, nsmall = 2)` \\
  \bottomrule
\end{tabular}}
\quad
\subfloat[Surface code]{\begin{tabular}{ c c c c c}
  \toprule
   Task & \multicolumn{3}{c}{Signal} \\
   \cmidrule(lr){2-4}
   & none  & visual & textual & All \\
   \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5}
  Control & `r format(mean(subset(data, signal=='n' & task=='c')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='c')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='c')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='c')$comp_C),digits = 2, nsmall = 2)`\\
  Verbal & `r format(mean(subset(data, signal=='n' & task=='t')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='t')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='t')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='t')$comp_C),digits = 2, nsmall = 2)`\\
  Visual & `r format(mean(subset(data, signal=='n' & task=='v')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='v')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='v')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='v')$comp_C),digits = 2, nsmall = 2)`\\
  Spatial & `r format(mean(subset(data, signal=='n' & task=='s')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='s')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='s')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='s')$comp_C),digits = 2, nsmall = 2)`\\
  \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5}
  All & `r format(mean(subset(data, signal=='n')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t')$comp_C),digits = 2, nsmall = 2)` & `r format(mean(data$comp_C),digits = 2, nsmall = 2)` \\
  \bottomrule
\end{tabular}}
\quad
\subfloat[Semantic]{\begin{tabular}{ c c c c c}
  \toprule
   Task & \multicolumn{3}{c}{Signal} \\
   \cmidrule(lr){2-4}
   & none  & visual & textual & All \\
   \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5}
  Control & `r format(mean(subset(data, signal=='n' & task=='c')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='c')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='c')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='c')$comp_S),digits = 2, nsmall = 2)`\\
  Verbal & `r format(mean(subset(data, signal=='n' & task=='t')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='t')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='t')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='t')$comp_S),digits = 2, nsmall = 2)`\\
  Visual & `r format(mean(subset(data, signal=='n' & task=='v')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='v')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='v')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='v')$comp_S),digits = 2, nsmall = 2)`\\
  Spatial & `r format(mean(subset(data, signal=='n' & task=='s')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='s')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='s')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='s')$comp_S),digits = 2, nsmall = 2)`\\
  \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5}
  All & `r format(mean(subset(data, signal=='n')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t')$comp_S),digits = 2, nsmall = 2)` & `r format(mean(data$comp_S),digits = 2, nsmall = 2)` \\
  \bottomrule
\end{tabular}}
\quad
\subfloat[Inference]{\begin{tabular}{ c c c c c}
  \toprule
   Task & \multicolumn{3}{c}{Signal} \\
   \cmidrule(lr){2-4}
   & none  & visual & textual & All \\
   \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5}
  Control & `r format(mean(subset(data, signal=='n' & task=='c')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='c')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='c')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='c')$comp_I),digits = 2, nsmall = 2)`\\
  Verbal & `r format(mean(subset(data, signal=='n' & task=='t')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='t')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='t')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='t')$comp_I),digits = 2, nsmall = 2)`\\
  Visual & `r format(mean(subset(data, signal=='n' & task=='v')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='v')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='v')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='v')$comp_I),digits = 2, nsmall = 2)`\\
  Spatial & `r format(mean(subset(data, signal=='n' & task=='s')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v' & task=='s')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t' & task=='s')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, task=='s')$comp_I),digits = 2, nsmall = 2)`\\
  \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5}
  All & `r format(mean(subset(data, signal=='n')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='v')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(subset(data, signal=='t')$comp_I),digits = 2, nsmall = 2)` & `r format(mean(data$comp_I),digits = 2, nsmall = 2)` \\
  \bottomrule
\end{tabular}}
\caption{Participants performance across conditions}
\end{table}
